Analyzing the impact of social attributes on commit integration success

### 2017-03-24 Paper/MSRChallenge2017.tex
added the last recommended related work
added the counts to section B and C along with justification to section C

\vspace{1ex}
\noindent\textbf{Related work:}
The most similar related work to this paper is a case study investigating how
social, technical, coordination, and prior-certification factors affect build
success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
focused on one project and measured experience as the number of contributions to
that project while our study focuses on a wide range of open source projects and
measures experience through developers' profile information.
Another study investigated the relationship between authors, files in project,
and team organization when predicting build
success on an IBM project with 151 developers.  The study found that as the
number of authors or files in a build increases, the probability of build
success decreases~\cite{Kwan11}.
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast, we focus on the relationship between independent social 
attributes and continuous integration success.

@@

These social factors are all factors that are tied to a GitHub user's profile
and that are generally correlated with user time and engagement with the site.
Thus, we use them as a proxy for
experience.
We also added one item from the MSR Challenge data set, indicating
whether the commit's developer is a core member  
of the associated project.

@@

Based on the decision tree results, we noticed that core team members where
important when classifying build success, so we decided to investigate if core
team members have greater build success rates.
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% of the builds in the data set and 75.58\% of those builds
passed.  Non-core team members triggered 10.61\% of the builds in the data set
and 64.70\% of the builds passed.  This shows that core team members are more
likely to have a successful build integration than non-core team members.

@@

We also investigated whether developers with followers were more likely to have a
successful build integration, since followers may be seen as vouching for
the developer's abilities.  We specifically investigated if a developer with 
followers was more likely to pass the build in the data set without 
downsampling.  We found that only 0.87\% of the
contributions in the data set was performed by developers with zero 
followers (excluding the developers in which we were not able to extract profile
information for). We found that 99.13\% of the contributions were performed by
developers with at least one or more followers.
Developers with 0 followers had a successful build commit 68.49\%
of the time.  Developers with one or more followers were successful 74.78\% of
the time.

We also investigated developers with a large number of followers (1000 or more
followers).  We found that 6.94\% of the contributions in the data set were
performed by developers with 1000 or more followers.  We found that these
contributions had a 78.61\% success rate.  These results show that developers
with more followers are more likely to have a successful integration build.

>>>>

\vspace{1ex}
\noindent\textbf{Related work:}
The most similar related work to this paper is a case study investigating how
social, technical, coordination, and prior-certification factors affect build
success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
focused on one project and measured experience as the number of contributions to
that project while our study focuses on a wide range of open source projects and
measures experience through developers' profile information.
Another study investigated the relationship between authors, files in project,
and team organization when predicting build
success on an IBM project with 151 developers.  The study found that as the
number of authors or files in a build increases, the probability of build
success decreases~\cite{Kwan11}. Another investigation used the same dataset and
found that team structures affected the teams' build success rate~\cite{Wolf09}.
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast, we focus on the relationship between independent social 
attributes and continuous integration success.

@@

These social factors are all factors that are tied to a GitHub user's profile
and that are generally correlated with user time and engagement with the site.
Thus, we use them as a proxy for
experience. If we were unable to find information about an author than we
assigned the commit empty values for these factors.
We also added one item from the MSR Challenge data set, indicating
whether the commit's developer is a core member  
of the associated project.

@@

Based on the decision tree results, we noticed that core team members where
important when classifying build success, so we decided to investigate if core
team members have greater build success rates.
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set and 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set
and 64.70\% (25479/39381) of the builds passed.  This shows that core team 
members are more
likely to have a successful build integration than non-core team members.

@@

We also investigated whether developers with followers were more likely to have a
successful build integration, since followers may be seen as vouching for
the developer's abilities.  We specifically investigated if a developer with 
followers was more likely to pass the build in the data set without 
downsampling.  We first investigated whether developers with one or more followers
were more likely to pass the build than developers without any followers, to
verify the assumption that followers vouch for a developer's abilities. To
investigate this question, we removed the commits without author profile
information (20374 builds which reduced the total build count from 371208 to
350834). We found 
that only 0.87\% (3059/350834) of the
contributions in the data set were performed by developers with zero 
followers (excluding the developers in which we were not able to extract profile
information for). We found that 99.13\% (347775/350834) of the contributions 
were performed by
developers with at least one or more followers.
Developers with 0 followers had a successful build commit 68.49\% (2095/3059)
of the time.  Developers with one or more followers were successful 74.78\%
(260056/347775) of the time.

We also investigated developers with a large number of followers (1000 or more
followers).  We found that 6.94\% (24347/350834) of the contributions in the 
data set were
performed by developers with 1000 or more followers.  We found that these
contributions had a 78.61\% (19138/24347) success rate.  These results show 
developers
with more followers are more likely to have a successful integration build.
